\thetitle

### 2008-02-01 models.tex
Updates.

\multirow{8}{*}[2.5pt]{\class{Node}}

@@

\raisebox{1.5pt}{$\centerdot$} session start time assigned from trace \\
\raisebox{1.5pt}{$\centerdot$} each node corresponds to a specific trace node with associated trace flows \\

@@

\raisebox{1.5pt}{$\centerdot$} session start time randomly assigned from pool of trace session start times \\

@@

\raisebox{1.5pt}{$\centerdot$} session start time assigned according to Poisson arrival model \\

@@

\raisebox{1.5pt}{$\centerdot$} nodes have the mean number of generic flows

>>>>

\multirow{8}{*}[2.5pt]{\class{Session}}

@@

\raisebox{1.5pt}{$\centerdot$} start time assigned from trace \\
\raisebox{1.5pt}{$\centerdot$} session corresponds to a specific trace node with associated trace flows \\

@@

\raisebox{1.5pt}{$\centerdot$} start time randomly assigned from pool of trace session start times \\

@@

\raisebox{1.5pt}{$\centerdot$} start time assigned according to Poisson arrival model \\

@@

\raisebox{1.5pt}{$\centerdot$} sessions all have the mean number of generic flows
